The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-30 manuscript/manuscript.Rnw
refer to how the lineage spec. analyses were done

\subsection{Comparative Analysis of Gene Expression}

@@

Using a mixed-effects linear model to account for repeated testing of
\human and \mouse, we identified multiple genes which are
differentially expressed in the \human lineage in comparison to all
other lineages (\cref{tab:human_lineage_specific}, Supplemental
\cref{tab:human_lineage_specific_all}). These genes include multiple
genes which are thought to be involved in pre-eclampsia. Notably,
\ac{CRH} (FDR=\Sexpr{hum.all.lin.spec["CRH",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["CRH",`Fold Change`]}, Supplemental
\cref{fig:crh_evolution_tree}), has been shown to be more highly
expressed in placentas from pre-eclamptic pregnancies
\cite{Petsas.ea2012:Aberrantexpressionofcorticotropin-releasing,Paiva.ea2011:MeasurementofmRNAtranscripts},
where it is hypothesized to activate decidual macrophages. Likewise,
\ac{KISS1} (\Sexpr{hum.all.lin.spec["KISS1",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["KISS1",`Fold Change`]}, Supplemental
\cref{fig:kiss1_evolution_tree}) also shows increased expression in
pre-eclamptic placentas, and is
involved in modulating trophoblast invasion~%
\cite{Vazquez-Alaniz.ea2011:Comparativeexpressionprofilesfor}. Two other genes,
\ac{PAPPA} (\Sexpr{hum.all.lin.spec["PAPPA",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["PAPPA",`Fold Change`]} Supplemental
\cref{fig:pappa_evolution_tree}) and \ac{ADAM12}
(\Sexpr{hum.all.lin.spec["ADAM12",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["ADAM12",`Fold Change`]}, Supplemental
\cref{fig:adam12_evolution_tree}) are also differentially expressed
but are negatively correlated with pre-eclampsia~%
\cite{Spencer.ea2008:ADAM12sinmaternalserum}.

>>>>

\subsection{Comparative Analysis of Gene Expression}
\label{sec:comp-analys-gene}

@@

Using a type-III ANOVA to account for repeated testing of
\human and \mouse (see \cref{sec:comp-analys-gene} for details), we identified multiple genes which are
differentially expressed in the \human lineage in comparison to all
other lineages (\cref{tab:human_lineage_specific}, Supplemental
\cref{tab:human_lineage_specific_all}). These genes include multiple
genes which are thought to be involved in pre-eclampsia. Notably,
\ac{CRH} (FDR=\Sexpr{hum.all.lin.spec["CRH",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["CRH",`Fold Change`]}, Supplemental
\cref{fig:crh_evolution_tree}), has been shown to be more highly
expressed in placentas from pre-eclamptic pregnancies
\cite{Petsas.ea2012:Aberrantexpressionofcorticotropin-releasing,Paiva.ea2011:MeasurementofmRNAtranscripts},
where it is hypothesized to activate decidual macrophages. Likewise,
\ac{KISS1} (\Sexpr{hum.all.lin.spec["KISS1",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["KISS1",`Fold Change`]}, Supplemental
\cref{fig:kiss1_evolution_tree}) also shows increased expression in
pre-eclamptic placentas, and is
involved in modulating trophoblast invasion~%
\cite{Vazquez-Alaniz.ea2011:Comparativeexpressionprofilesfor}. Two other genes,
\ac{PAPPA} (\Sexpr{hum.all.lin.spec["PAPPA",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["PAPPA",`Fold Change`]} Supplemental
\cref{fig:pappa_evolution_tree}) and \ac{ADAM12}
(\Sexpr{hum.all.lin.spec["ADAM12",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["ADAM12",`Fold Change`]}, Supplemental
\cref{fig:adam12_evolution_tree}) are also differentially expressed
but are negatively correlated with pre-eclampsia~%
\cite{Spencer.ea2008:ADAM12sinmaternalserum}.
